Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-10 demystify.tex
updates

    \item Miscs and FAQS
        \begin{itemize}
          \item Why you were rejected (\autoref{sec:why-rejected}). One potential reason is because you're applying to AI/ML, a super competitive field in recent years with many applicants.
          \item Why rejection letters are sent so late? (\autoref{sec:late-rejection}). Grad programs often wait for the accepted students to make their decisions, typically by April 15, before sending out rejection letters.

          \item Increasing admission chance by being unique and standing out (\autoref{sec:improve-your-chance}).
          \item It take about 10 minutes to review an application (\autoref{sec:ievaluate}).
          \item Being a minority can help (\autoref{sec:urm}).
          \item You can successfully apply to CS PhD even if you have non-CS background (\autoref{sec:non-stem}).
          \item You do not need an MS degree (\autoref{sec:msrequirement}), and CS PhD takes about 5--7 years (\autoref{sec:time}). Compared to other countries, CS PhD in the US does not require an MS degree but has a longer PhD study time (\autoref{sec:non-us-differences}).
          \item How do you call your professors? In many cases, just by first names! (\autoref{sec:address})
          \item Your entire PhD program costs about \$400K in total, but you \emph{do not} pay for it (\autoref{sec:ra-cost})
          \item Ask your prof. if they can buy computer equipment and such for your research (\autoref{sec:buying-equipment}).
          %\item Despite some miserable stories on social media, many PhD students have good mentors, supportive lab mates, healthy working environment ... and are happy (\autoref{sec:happy}).
        \end{itemize}

>>>>

    \item Miscs and FAQS
        \begin{itemize}
          \item Why you were rejected (\autoref{sec:why-rejected}). One potential reason is because you're applying to AI/ML, a super competitive field in recent years with many applicants.

          \item Why rejection letters are sent so late? (\autoref{sec:late-rejection}). Grad programs often wait for the accepted students to make their decisions, typically by April 15, before sending out rejection letters.

          \item Increasing admission chance by being unique and standing out (\autoref{sec:improve-your-chance}).
          \item It take about 10 minutes to review an application (\autoref{sec:ievaluate}).
          \item Being a minority can help (\autoref{sec:urm}).
          \item You can successfully apply to CS PhD even if you have non-CS background (\autoref{sec:non-stem}).
          \item You do not need an MS (\autoref{sec:msrequirement}), and CS PhD takes about 5--7 years (\autoref{sec:time}). Compared to other countries, CS PhD in the US does not require an MS degree but has a longer PhD study time (\autoref{sec:non-us-differences}).
          \item What should you call your profs.? (\autoref{sec:address}) Many possibilities (e.g., prof., Dr., and even their firstnames), but probably not Mr. or Mrs.
          \item Your entire PhD program costs about \$400K in total, but you \emph{do not} pay for it (\autoref{sec:ra-cost})
          \item Ask your prof. if they can buy computer equipment and such for your research (\autoref{sec:buying-equipment}).
          %\item Despite some miserable stories on social media, many PhD students have good mentors, supportive lab mates, healthy working environment ... and are happy (\autoref{sec:happy}).
        \end{itemize}
